PANCHANGE_analysis

### 2020-09-03 PANCHANGE_analysis.Rmd
PCL regression chunks amended. Outcome variable currently N symptoms that participants report being impacted by the pandemic (likely will want to change this?).

### PCL
Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model 0a}
pcl_retro_model0a <- lm(
  formula = pcl.diff_score_base_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1a}
pcl_retro_model1a <- lm(
  formula = pcl.diff_score_base_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.diff_score_base_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)

>>>>

### PCL

++MD: Not sure if this is how we want to run the PCL regression - the outcome variable I've included is "How many PCL items the participants report are related to the pandemic", but I think we might want a more nuanced approach than this.

```{r recode PCL retro variable as numeric}
dat.retro <- dat.retro %>% 
  mutate(
    pcl.sum_score_retro = 
      as.numeric(pcl.sum_score_retro_raw)
  )
```

Model 0a: Disorder_hierarchical, Unadjusted
```{r PCL retro Model 0a}
pcl_retro_model0a <- lm(
  formula = pcl.sum_score_retro ~ 
    Disorder_hierarchical,
  data = dat.retro)

@@

Model 0b: Overlapping disorders, Unadjusted
```{r PCL retro Model 0b}
pcl_retro_model0b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder,
  data = dat.retro)

@@

Model 1a: Disorder hierarchical, Adjusted
  Model 0a + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1a}
pcl_retro_model1a <- lm(
  formula = pcl.sum_score_retro ~ 
    Disorder_hierarchical + 
    Gender_collapsed + 
    age_category + 
    Ethnicity_collapsed + 
    time_diff_sign_up_coping,
  data = dat.retro)

@@

Model 1b: Overlapping disorders, Adjusted
  Model 0b + Sex + Age + Ethnicity_collapsed + Time registration and baseline
```{r PCL retro Model 1b}
pcl_retro_model1b <- lm(
  formula = pcl.sum_score_retro ~
    anxiety_disorders +
    depressive_disorders +
    eating_disorders +
    obsessive_compulsive_disorders +
    psychotic_disorders +
    mhd.mania_hypomania_bipolar_or_manicdepression +
    mhd.posttraumatic_stress_disorder_ptsd +
    autism_spectrum_disorder +
    mhd.attention_deficit_hyperactivity_disorder +
    mhd.personality_disorder +
    Gender_collapsed + age_category + Ethnicity_collapsed + time_diff_sign_up_coping,
  data = dat.retro)
